Assessing Fire Response Efficiency and the Crucial Role of Protection Systems in Reducing Damage

### 2024-09-23 paper/paper.qmd
update paper structure in intro

In this paper we visualize Toronto's Fire Incidents data. The remainder of the paper is structured as follows. [Section 2](#sec-data) discusses the raw and cleaned data, as well as the summary statistic. Then in [Section 2.2](#sec-data-tfs) and [Section 2.3](#sec-data-fpe), We discuss the trend and distribution of TFS response time and fire protection equipment presence. In [Section 3](#sec-discuss), we provide analysis of the trend and correlation in [Section 2](#sec-data), as well as the limitations and future directions in resolving urban fire incidents.

>>>>

In this paper we visualize Toronto's Fire Incidents data. The remainder of the paper is structured as follows. @sec-data discusses the raw and cleaned data, as well as the summary statistic. Then in @sec-data-tfs and @sec-data-fpe, We discuss the trend and distribution of TFS response time and fire protection equipment presence. In @sec-discuss, we provide analysis of the trend and correlation in @sec-data, as well as the limitations and future directions in resolving urban fire incidents.
